\documentclass[12pt]{article}
\usepackage[a4paper]{geometry}
\usepackage{amsmath}
\geometry{top=1.0in, bottom=1.0in, left=1.0in, right=1.0in} % Sets the margins
\setlength{\parindent}{0pt} % Fixes the paragraph spacing problem
\renewcommand*\arraystretch{1.5}

\begin{document}

\begin{center}
        \LARGE{\textbf{Informed Consent}}
        \line(1,0){500}
\end{center}

You are invited to participate in a study conducted by Singularity Software. We hope to learn the ways in which our software (the Siftables Emulator) is more or less easy-to-use than (Sifteo cube developer) Sifteo Inc.'s Siftulator. You were selected as a possible participant in this study because of your familiarity with software development and the process it entails. \\\\
If you decide to participate, we will ask you to complete a series of tasks within both emulators and then to report on your experience. This will take no more than 30 minutes and will only be conducted once. There are no risks inherent in your study participation. \\\\
Any personally-identifiable information that is obtained in connection with this study will remain confidential and will be disclosed only with your advance permission. Should the data be published --- either for the purpose of obtaining course credit in CSSE 371 or for other puproses --- no personally-identifiable information will be disclosed. Your participation in this usability study is voluntary. By completing the survey, you are voluntarily agreeing to participate. You are free to skip any particular question you do not wish to answer for any reason. \\\\
If you have any questions at any point during the study or thereafter, please contact any member of the Singularity Software project team: Alex Mullans at mullanaj@rose-hulman.edu, Ruben Rodriguez at rodrigrd@rose-hulman.edu, Ethan Veatch at veatchje@rose-hulman.edu, or Kurtis Zimmerman at zimmerka@rose-hulman.edu.\\\\
If you have any questions about your rights as a research subject or if you feel you've been placed at risk, you may contact the Institutional Reviewer, Robert Throne, by mail at CM 114, by phone at (812) 877-8414, or by email at throne@rose-hulman.edu.
\\\\\\

\begin{tabular}{l l}
  \line(1,0){100} &
  \hspace{.8in} \line(1,0){275} \\

  \textbf{Date} &
  \hspace{.8in} \textbf{Signature} \\

  \\ \\

  &
  \hspace{.8in} \line(1,0){275} \\

  &
  \hspace{.8in} \textbf{Signature of Investigator}
\end{tabular}

\end{document}
