\documentclass[12pt]{article}
\usepackage[a4paper]{geometry}
\usepackage{amsmath}
\geometry{top=1.0in, bottom=1.0in, left=1.0in, right=1.0in} % Sets the margins
\setlength{\parindent}{0pt} % Fixes the paragraph spacing problem
\renewcommand*\arraystretch{1.5}

\begin{document}

\begin{center}
        \LARGE{\textbf{Informed Consent}}
        \line(1,0){500}
\end{center}

You are invited to participate in a study conducted by Singularity Software.  We hope to learn the ways in which our software is more or less easy-to-use than Sifteo's Siftulator.  You were selected as a possible participant in this study because of your familiarity with software development and the process it entails. \\\\
If you decide to participate, we will ask you to complete a series of tasks within both emulators and report on your experience.  This will take no more than 30 minutes and will only be conducted once.  There are no risks to you by participating in this study. \\\\
Any information that is obtained in connection with this study and that can be identified with you will remain confidential and will be disclosed only with your permission. If you give us your permission by signing this document, we plan to disclose all pertinent information to the clients --- Mr. Tim Ekl and Mr. Eric Stokes --- the instructor advising in this course (Dr. Sriram Mohan); additionally, the data collected from your study will be published in milestone documents and a presentation to be shown to other groups enrolled in the course. \\\\
If you have any questions at any point during the study or thereafter, please contact any member of the Singularity Software project team, who will be happy to answer them. \\\\\\

\begin{tabular}{l l}
  \line(1,0){100} &
  \hspace{.8in} \line(1,0){275} \\

  \textbf{Date} &
  \hspace{.8in} \textbf{Signature} \\

  \\ \\

  &
  \hspace{.8in} \line(1,0){275} \\

  &
  \hspace{.8in} \textbf{Signature of Investigator}
\end{tabular}

\end{document}
